Who needs privacy?

### 2024-02-08 analyses.RmD
- Rendered website

fig_reg <- ggplot(
  tab_reg, aes(x = Estimate, y = Predictor, color = relevant)
  ) + 
  coord_cartesian(xlim = c(-.7, .3)) +
  geom_vline(xintercept = 0, lwd = .5, colour = "darkgrey") + 
  geom_vline(xintercept = -.1, lwd = .5, colour = "darkgrey", linetype = "dashed") + 
  geom_vline(xintercept = .1, lwd = .5, colour = "darkgrey", linetype = "dashed") + 
  geom_errorbarh(
    aes(xmin = CI_low, xmax = CI_high),
    lwd = .5, height = .4, position = position_dodge(-.7)
    ) +
  geom_point(size = 1, position = position_dodge(-.7)) +
#   geom_pointrange(aes(xmin = CI_low, xmax = CI_high), size = .2) + 
  scale_x_continuous(
    breaks = c(-.6, -.4, -.2, 0, .2, .4),
    labels = c("-.6", "-.4", "-.2", "0", ".2", ".4")
    ) + 
  scale_y_discrete(limits=rev) +
  scale_color_manual(values = c("grey", "black")) +
  labs(
    title = "Predicting the need for privacy",
    x = "Correlation coefficient"
    ) +
  # theme_minimal() +
  theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    text = element_text(size = 14),
    axis.text.y = element_text(hjust = 1),
    axis.text.x = element_text(size = 10),
    legend.position = "none"
    ) + 
  facet_grid(category ~ `Need for privacy`, scales = "free_y")

>>>>

fig_cor <- ggplot(
  tab_cor, aes(x = Estimate, y = Predictor, color = relevant)
  ) + 
  coord_cartesian(xlim = c(-.7, .3)) +
  geom_vline(xintercept = 0, lwd = .5, colour = "darkgrey") + 
  geom_vline(xintercept = -.1, lwd = .5, colour = "darkgrey", linetype = "dashed") + 
  geom_vline(xintercept = .1, lwd = .5, colour = "darkgrey", linetype = "dashed") + 
  geom_errorbarh(
    aes(xmin = CI_low, xmax = CI_high),
    lwd = .5, height = .4, position = position_dodge(-.7)
    ) +
  geom_point(size = 1, position = position_dodge(-.7)) +
#   geom_pointrange(aes(xmin = CI_low, xmax = CI_high), size = .2) + 
  scale_x_continuous(
    breaks = c(-.6, -.4, -.2, 0, .2, .4),
    labels = c("-.6", "-.4", "-.2", "0", ".2", ".4")
    ) + 
  scale_y_discrete(limits=rev) +
  scale_color_manual(values = c("grey", "black")) +
  labs(
    title = "Predicting the need for privacy",
    x = "Correlation coefficient"
    ) +
  # theme_minimal() +
  theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    text = element_text(size = 14),
    axis.text.y = element_text(hjust = 1),
    axis.text.x = element_text(size = 10),
    legend.position = "none"
    ) + 
  facet_grid(category ~ `Need for privacy`, scales = "free_y")

### 2024-02-08 index.Rmd
- Rendered website

- You can either read the paper [in your browser](proposal.html) or download it as [pdf](proposal.pdf). 
- You can also find the detailed code and summaries of the [planned analyses](analyses.html) reported in the paper
- Once finished, you will also be able to find [additional analyses](analyses_additional.html) not reported in the paper.

>>>>

- You can either read the paper [in your browser](proposal.html) or download it as [pdf](proposal.pdf). 
- You can also find the detailed code and summaries of the [analyses](analyses.html) reported in the paper

### 2024-02-08 proposal.Rmd
- Rendered website

documentclass     : "apa6"
# classoption       : "man"
# output: html_document
output            : papaja::apa6_pdf
# output            : papaja::apa6_word

@@

```{r setup, include=F}
# devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
packages <- c("devtools", "english", "ggplot2", "kableExtra", "lavaan", 
              "magrittr", "papaja", "semPlot", "simsem", "td", "tidyverse")
lapply(packages, library, character.only = TRUE)
load("data/workspace.RData")

>>>>

documentclass     : "apa6"
# classoption       : "man"
output: html_document
# output            : papaja::apa6_pdf
# output            : papaja::apa6_word

@@

```{r setup, include=F}
# devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
packages <- c("devtools", "english", "ggplot2", "kableExtra", "lavaan", 
              "magrittr", "papaja", "semPlot", "simsem", "td", "tidyverse")
lapply(packages, library, character.only = TRUE)
load("data/workspace_2.RData")
